---
output: 
  html_document:
    code_folding: show
    df_print: paged
    highlight: zenburn
    
---

<style>
.table-hover > tbody > tr:hover { 
  background-color: #0080ff;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
library(tidyverse)
library(janitor)
library(broom)
library(knitr)
library(kableExtra)
library(plotly)
```


# <span style="color:black"> Exam 3 </span> {.tabset}



## <span style="color:black"> Faculty Salaries </span> {.tabset}



### <span style="color:black">  1. Clean and visualize faculty salaries </span> 



Cleaning up the data : 

The data needs to be split into 3 new data sets one for salary values, one for comp values, and one for the number of each position. 

```{r echo=TRUE, message=FALSE, warning=FALSE}
dat <- read.csv('./FacultySalaries_1995.csv')

salary <- dat %>% select(FedID,UnivName,State,Tier,
                         AvgFullProfSalary,AvgAssocProfSalary,AvgAssistProfSalary,AvgProfSalaryAll) %>%
  pivot_longer(cols=-c(FedID,UnivName,Tier,State),
               names_to = 'Rank',
               values_to = 'salary') %>% 
  mutate(Rank=str_remove(Rank,'Prof'),
         Rank =str_remove(Rank,'Avg'),
         Rank=str_remove(Rank,'Salary'))


comp <- dat %>% select(FedID,UnivName,State,Tier,
                       AvgFullProfComp,AvgAssocProfComp,AvgAssistProfComp,AvgProfCompAll) %>%
  pivot_longer(cols=-c(FedID,UnivName,Tier,State),
               names_to = 'Rank',
               values_to = 'comp')%>% 
  mutate(Rank=str_remove(Rank,'Prof'),
         Rank =str_remove(Rank,'Avg'),
         Rank=str_remove(Rank,'Comp'))


num <- dat %>% select(FedID,UnivName,State,Tier,
                      NumFullProfs,NumAssocProfs,NumFacultyAll,NumInstructors,NumAssistProfs) %>%
  mutate(ProfAll=NumFullProfs+NumAssocProfs+NumAssistProfs) %>% 
  pivot_longer(cols=-c(FedID,UnivName,Tier,State),
               names_to = 'Rank',
               values_to = 'num')%>% 
  mutate(Rank=str_remove(Rank,'Prof'),
         Rank=str_remove(Rank,'Num'),
         Rank=if_else(str_ends(Rank,'s'),str_sub(Rank,end = -2L),Rank))
  


tidy <-salary %>% 
  full_join(num) %>% 
  full_join(comp)

kable(head(tidy),format = 'html') %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))

```
Now that the data is tidy we can work on recreating the given graph

```{r message=FALSE, warning=FALSE}
tidy%>%
  filter(Rank=='Assist'|Rank=='Assoc'|Rank=='Full') %>%
  filter(Tier!='VIIB') %>% 
  
 ggplot(aes(y=salary,x=Rank,fill=Rank))+
  facet_wrap(vars(Tier))+
  geom_boxplot()+
  theme(axis.text.x = element_text(angle = 90,vjust = .5))



```

___

### <span style="color:black"> 2.Build an ANOVA model for the data </span>

```{r warning=FALSE}
aovm <- aov(data = tidy,
    salary~State+Tier+Rank) %>% 
  tidy()


kable(aovm,format = 'html') %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))

```
This anova model was testing the null hypothesis that State, Tier, and Position have no impact on salary. Based on the p values produced by this test(~2*10^16 for all variables) we can reject the null hypothesis for all three variables and conclude that state, tier, and rank all impact salary.



## <span style="color:black"> Juniper Oils </span> {.tabset}



### <span style="color:black"> 3. Tidy the juniper oils data </span>
```{r warning=FALSE}
 chemname<- c("alpha-pinene","para-cymene","alpha-terpineol","cedr-9-ene",
             "alpha-cedrene","beta-cedrene","cis-thujopsene","alpha-himachalene",
             "beta-chamigrene","cuparene","compound.1","alpha-chamigrene","widdrol",
             "cedrol","beta-acorenol","alpha-acorenol","gamma-eudesmol","beta-eudesmol",
             "alpha-eudesmol","cedr-8-en-13-ol","cedr-8-en-15-ol","compound.2",
             "thujopsenal")
chemname <- str_replace_all(chemname,'-','.')

oils <- read.csv('./Juniper_Oils.csv') 

t_oil <- oils %>% pivot_longer(cols = chemname,
                      names_to = 'chemical_id',
                      values_to ='concentration' )

head(t_oil)
```

___

### <span style="color:black"> 4. Plot concentrations over time for all chemicals </span>
```{r message=FALSE, warning=FALSE}
t_oil %>% 
  ggplot(aes(y=concentration,x=YearsSinceBurn))+
  geom_smooth()+
  facet_wrap(vars(chemical_id),scales = 'free')

```

___

### <span style="color:black"> 5.What chemicals are infuenced by time? </span>

```{r warning=FALSE}
oilm<- glm(data = t_oil,concentration~YearsSinceBurn*chemical_id)

significant <- tidy(oilm) %>% 
  filter(p.value<=0.05)%>% 
  mutate(term=str_remove(term,'chemical_id'),term=str_remove(term,'YearsSinceBurn:'))

kable(significant,format = 'html')%>%
  kable_styling(bootstrap_options = c("striped", "hover"))
  
```
This model found that the concentrations of the chemicals alpha.cedrene,cedr.8.en.13.o, cedrol, cis.thujopsene, widdrol, and cis.thujopsene are all significantly affected by time.

___
